---
title: "Creating Courses from Scratch"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating Courses from Scratch}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(didactr)
auth_file = "../tests/testthat/googlesheets_token.rds"
if (file.exists(auth_file)) {
  didactr_auth(token_file = auth_file)
} else {
  x = didactr_auth()
}
stopifnot(check_didactr_auth())
```

```{r setup}
library(didactr)
```



# Setting up a Temporary Course

Here we will work in temporary directories in `R`.  In your cases, you'd want to change `root_path` to a folder on your computer where your class will live.  The class folder will be in `root_path/course_name`.  Here we will call our course name `test`.  For course names, these should not have any spaces; all slide decks will have `course_name` prepended on them.  The `create_course` function will create the course.  FYI - the `start_course` function is identical to `create_course`.

```{r}
root_path = tempfile()
course_name = "test"
sc = create_course(course_name, root_path)
sc
```

We see the paths that have been created for the project.

## Leanpub courses

If you've never created a Leanpub, the structure is that the top-level folder is a course.  The course has the following components:

1. A `manuscript` folder with a Markua/`md` file for each lesson.  [Markua](https://leanpub.com/markua/read) is a subset of Markdown, but has additional elements for quizzes and other teaching.
2. A `Book.txt` in the `manuscript` folder. This `Book.txt` is a simple text file that determines the order of the lessons, with one line for each `.md` file. The suffix needs to be included and the file names need to match exactly.
3. A `manuscript/resources` folder, which contains an `images` sub-folder with `png`/images for each lesson.  We will not use these in this workflow as all images are directly encoded from a Google Slide deck.

## Courses using `didactr`

In `didactr`, we have additional components
1. A `scripts` folder which contains `.md` files that correspond to the spoken words to be said over the slides.  These are plain text (not markdown) and "special" words need to be phonetically spelled, such as `R Studio`.  Each newline separates slides, so there needs to be the same number of non-empty lines as the number of slides in the slide deck.
2.  A `manuscript/resources/videos` folder which contains the synthesized videos from the Google Slide deck and the script.  The audio is generated by Amazon Polly.  
  - If you want to create the videos on your own, you need to create an Amazon account.  See https://github.com/cloudyr/aws.signature for more information.

### A note on authorization

You must authorize `didactr` to be able to read and copy on your Google Drive/Google Slides.  The `create_lesson` function will authorize using OAuth for this and other things.  Authorization for YouTube will be used later for uploading videos.  We bundled all the authorizations into one in `didactr` so that you only have to authorize once.  If you do not want to authorize for YouTube, that is fine for now.

## Keeping Repositories Light
As videos can be very large, we likely don't want to upload them to spaces like GitHub. As such, by default, the videos directory is excluded from `git`:
```{r}
readLines(file.path(sc$course_dir, ".gitignore"))
```

Now we will create a lesson in that course.  There are a few ways to do this.  If you have Markdown/`md` files already and have a `Book.txt`, which is required for Leanpub, then you want to look at the `create_lessons_from_book` function.  As we are starting from **scratch**, we will assume you have at most a Google Slides deck, but this is not required.


## Starting with a Google Slide Deck

If you start with a Google Slide deck, you need the Slide ID.  If you don't have a deck, you can simply run the `create_lesson` command and it will create a Google Slide deck copy from one we provide.  Here you must supply a `lesson_name`.  This can have spaces if you want and will be the title of the lesson.  We will pass the course directory in here from our `sc` object, otherwise it assumes we are creating this in the current working directory.  The `slide_id` is the slide identifier for a Google Slide deck.  The ID can be found after `https://docs.google.com/presentation/d/` in the URL when you are editing the slides.  If you do not specify a slide ID, the `make_slide_deck` argument determines if you would like to create a slide deck.  The `md_file` argument allows you to override the standard naming convention we recommend, the `rmd` argument says whether you'd like to use an Rmarkdown vs. Markdown document and `open` determines if you'd like to edit the document and script after creating it.  **NB:** if you're creating a slide deck, we are copying over a slide deck from a different Google Drive and may take a few seconds due to the Google Drive API.

```{r}
out = create_lesson(
  lesson_name = "How to Do Things",
  course_dir = sc$course_dir,
  make_slide_deck = TRUE,
  open = FALSE)
out
```

We see the output is the Markdown file, slide ID for the deck, and the output script file (to be spoken over the slides).  Here is the output of the MD file:

```{r}
readLines(out$md_file)
```

Notably, we see that any area of "Notes" in the Google Slide deck is copied to the manuscript.  This is also done for the `script`:

```{r}
readLines(out$script_file)
```

## Viewing the Lesson 

If you are using an `Rmd` instead of an `md`, you need to `knit` the `Rmd` to create the `md` and make sure an `md` was the output.  Now that you have the `md` file, you can run `leanpub_render` to view the output of the `md` as it should be shown on Leanpub.

```{r}
if (interactive()) {
  leanpub_render(out$md_file)
}
```

If you are including `png` or other files with **links** and not included in the `manuscript/resources/images` folder in your course, then you must specify the format before the Markdown.  For example if you want to include a PNG from Google Slides, we can use the following lines:

```yaml
{format: png}
![](https://docs.google.com/presentation/d/143gvqcynq_bl7iVd2G9yjumwJJkAy0S6CyNCsrJ2LgE/export/png?id=143gvqcynq_bl7iVd2G9yjumwJJkAy0S6CyNCsrJ2LgE&pageid=p)
```

## Specification for a Script

A script file must have as many non-empty lines as there are slides.  If you don't want any text read over the slide, simply add a simple semicolon `";"` or comman `","`.  

# Checking a Course

The `check_course` function is the main function for determining if the structure of the course is setup correctly.  This checks **a lot** of different folders and such.  If you've created the course using `create_course`, these should likely have been created already.  Videos and other resources _

```{r}
result = check_course(course_dir = sc$course_dir, check_youtube_links = FALSE)
result$course_summary
```
If there are multiple warnings, this may be due to the YouTube links not included, the Google Slide ID not included, or the number of paragraphs in the scripts not matching up with the number of slides.  

# Changes to Manuscript files

Now that you have a lesson created, you likely want to change the content and the slides over time.  Let's say you want to include a slide, you can use the `gs_slide_df` function.  The output is a `tibble` with a lot of elements.  You can extract `objectId` to grab the "page" identifier, which is unique to that specific slide in the deck.  Note, the ID and slide ID combination **together** make it unique over all of Google, not simply the page ID.  For example, most first slides have the ID `p`.

```{r}
slide_df = gs_slide_df(id = result$course_summary$id[1])
slide_df$objectId
```

## Code inside a text box

If you have code in a Google Slide deck and want to extract it, you must mark in the Google Slide Deck.  You can either:
1. You can add `#rstats` to the text box anywhere.
2. Right click the text box and add the title `#rstats` to the Alt-text.  Right click the text box → `Alt text...` → Title `#rstats`.

For example, we have a slide deck with some code and here is the output:
```{r}
out_rmd = create_lesson(
  lesson_name = "An example with some code",
  course_dir = sc$course_dir,
  slide_id = "1Tg-GTGnUPduOtZKYuMoelqUNZnUp3vvg_7TtpUPL7e8",
  extract_code = TRUE,
  rmd = TRUE,
  open = FALSE)
x = readLines(out_rmd$md_file)
ind = grep("```\\{r [^setup]", x)[1]
cat(x[(ind - 5):(ind + 14)], sep = "\n")
```

## Making Local Data

If you want to take the Google Slides and download them into individual PNGs so you can view them, the `gs_convert` takes in an ID and then converts the images to PNGs.  This requires the `convert` function and ImageMagick being installed.  If you use the `gs_convert(..., use_gs_ids = TRUE)`, the files will be named using the Google Slide page ID, which can allow you to "link" the image to the ID, so you can use

```yaml
{format: png}
![](https://docs.google.com/presentation/d/SLIDE_ID/export/png?id=SLIDE_ID&pageid=PAGE_ID)
```

in your manuscript files, shere `SLIDE_ID` is the Google Slide deck ID and `PAGE_ID` is the page ID given by the filename of the png when `use_gs_ids = TRUE`.  
